STA302 Final Project Proposal

### 2024-10-11 paper/proposal.qmd
Update proposal.qmd

>>>>

# Fit multiple linear regression model
model <- lm(average_playtime ~ price + positive_ratings + negative_ratings + developer + owners)

# Create Residuals vs Fitted Scatterplot to check Linearity, Uncorrelated Errors, and Constant Variance

y_value <- resid(model)
x_value <- fitted(model)

plot(x = x_value, y = y_value, main = "Residual vs. Fitted", xlab = "Fitted", ylab = "Residuals")

# Create Residuals vs each Quantitative Predictor scatterplot to check Linearity, Uncorrelated Errors, and Constant Variance

par(mfrow=c(1,3))

plot(x = data$price, y = y_value, main = "Residuals vs. Price", xlab = "Price", ylab = "Residuals")

plot(x = data$positive_ratings, y = y_value, main = "Residuals vs. Positive Ratings", xlab = "Positive Ratings", ylab = "Residuals")

plot(x = data$negative_ratings, y = y_value, main = "Residuals vs. Negative Ratings", xlab = "Negative Ratings", ylab = "Residuals")

# Create BoxPlot to check assumptions for Categorical Predictors

par(mfrow=c(1,2))

boxplot(y_value ~ data$developer , main="Residual vs Developer",
xlab="Developer", ylab="Residuals")

boxplot(y_value ~ data$owners , main="Residual vs Owners",
xlab="Owners", ylab="Residuals")

# Create Normal QQ Plot to check Normality assumption

qqnorm(y_value)
qqline(y_value)
